---
title: "statistics_for_prediction"
author: "Anamay Shetty"
date: "12/12/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rethinking)
theme_set(theme_minimal())
knitr::opts_chunk$set(echo = FALSE)
```

```{bash Converting to R-readable format, include = FALSE}
sed -e 's| Home |,Home |g'  -e 's|Y| Y|g' -e 's| *Y| Y|g' data/raw_bmat_results_tl.txt | tr "," "\n" > data/bmat_results_tl.txt
```

```{r Read in data file, include = FALSE}
df <- read_delim("data/bmat_results_tl.txt", delim = " ", col_names = c("Domicile", "Course", "Year", "Candidate", letters[1:8]), skip = 1) %>%
  unite("x", a:h, sep = " ") %>%
  mutate(x = str_remove_all(x, " NA")) %>%
  mutate(b = str_extract(x, "[0-9](.[0-9]|) [0-9](.[0-9]|)")) %>%
  separate(b, into = c("BMAT_Section_1", "BMAT_Section_2"), sep = " ", convert = TRUE) %>%
  mutate(Offer = ifelse(str_detect(x, "Y "), TRUE, FALSE)) %>%
  mutate(x = (str_remove(x, " ?(Y|) [0-9](.[0-9]|) [0-9](.[0-9]|)"))) %>%
  rename("College" = x) %>%
  mutate(BMAT_all = BMAT_Section_1 + BMAT_Section_2) %>%
  #group_by(College, Year) %>%
  #mutate(offer_fraction = sum(Offer)/n()) %>%
  #ungroup %>%
  select(Candidate, Offer, BMAT_all)
```

Statistics is a common feature of many science courses. I see statistics as solving two questions in science:

1. Using current data and knowledge, can we predict an outcome in other situations?

2. Using current data and knowledge, can we understand the underlying mechanisms which cause our outcomes of interest?

In a more concrete sense, question 1 in prediction - "What will the effects of giving drug A to person X be?" - whilst question 2 is a question of inference - "Is our scientific model of drug action correct given data about drug effects?".

These are often conflated, but I think prediction is something quite apart from inference, and this little piece is designed to really pull these apart - and ultimately show **why** they are so often conflated. We will tackle the question of inference in a separate piece. 

A bit of background. When I was first starting off as a very bor(ed/ing) Year 12/13 student in statistics, I was interested in this question of using the scores people got on a medical aptitude test - the BMAT - to predict whether they were going to get entry to medicine courses at university. 

Let's put ourselves in the shoes of someone who is coming to ask "What are my chances of getting into Cambridge?"

Our dataset we're going to use is the BMAT dataset, which has `nrow(df)` people applying to Cambridge colleges. 

```{r}
df %>%
  ggplot(aes(x = BMAT_all, y = as.numeric(Offer))) +
  geom_point()
```


```{r}
df %>%
  #mutate(bins = BMAT_all) %>%
  mutate(bins = round(BMAT_all)) %>%
  group_by(bins) %>%
  mutate(offer_fraction = mean(Offer), n = n()) %>%
  ggplot(aes(bins, offer_fraction)) +
  geom_point(aes(x = BMAT_all, y = as.numeric(Offer))) +
  geom_point(colour = "red") +
  geom_line(colour = "red")
```