---
title: "statistics_for_prediction"
author: "Anamay Shetty"
date: "12/12/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rethinking)
theme_set(theme_minimal())
knitr::opts_chunk$set(echo = FALSE)
```

```{bash Converting to R-readable format, include = FALSE}
sed -e 's| Home |,Home |g'  -e 's|Y| Y|g' -e 's| *Y| Y|g' data/raw_bmat_results_tl.txt | tr "," "\n" > data/bmat_results_tl.txt
```

```{r Read in data file, include = FALSE}
df <- read_delim("data/bmat_results_tl.txt", delim = " ", col_names = c("Domicile", "Course", "Year", "Candidate", letters[1:8]), skip = 1) %>%
  unite("x", a:h, sep = " ") %>%
  mutate(x = str_remove_all(x, " NA")) %>%
  mutate(b = str_extract(x, "[0-9](.[0-9]|) [0-9](.[0-9]|)")) %>%
  separate(b, into = c("BMAT_Section_1", "BMAT_Section_2"), sep = " ", convert = TRUE) %>%
  mutate(Offer = ifelse(str_detect(x, "Y "), TRUE, FALSE)) %>%
  mutate(x = (str_remove(x, " ?(Y|) [0-9](.[0-9]|) [0-9](.[0-9]|)"))) %>%
  rename("College" = x) %>%
  mutate(BMAT_all = BMAT_Section_1 + BMAT_Section_2) %>%
  #group_by(College, Year) %>%
  #mutate(offer_fraction = sum(Offer)/n()) %>%
  #ungroup %>%
  select(Candidate, Offer, BMAT_all)
```

Statistics is a common feature of many science courses. I see statistics as solving two questions in science:

1. Using current data and knowledge, can we predict an outcome in other situations?

2. Using current data and knowledge, can we understand the underlying mechanisms which cause our outcomes of interest?

In a more concrete sense, question 1 in prediction - "What will the effects of giving drug A to person X be?" - whilst question 2 is a question of inference - "Is our scientific model of drug action correct given data about drug effects?".

These are often conflated, but I think prediction is something quite apart from inference, and this little piece is designed to really pull these apart - and ultimately show **why** they are so often conflated. We will tackle the question of inference in a separate piece. 

A bit of background. When I was first starting off as a very bor(ed/ing) Year 12/13 student just getting interested in statistics, I went and worked one of the first things I did was to download a dataset of BMAT scores and medicine Offers and do an excercise in prediction. I imagined what I would say if someone came up to me and asked:

"Anamay I have <blah> BMAT score: what's my chances of getting into Cambridge?"

### Option 1: You're not going to get in

Let's say I gave you my dataset, but without the BMAT scores. You may think that there's no way you can answer the question posed, but we can!

The average fraction of applications which lead to offers is `r round(mean(df$Offer), 3)`. This means that if you knew nothing about the person, you should tell them they won't get in! After all, you'll be right roughly 75% of the time.

### Option 2: Let me find your score in my table

### Option 3: You'll get in if you do really well in the BMAT, but not if you do really *really* well on the BMAT

### Option 4: Let's use a model?



```{r}
df %>%
  ggplot(aes(x = BMAT_all, y = as.numeric(Offer))) +
  geom_point()
```


```{r}
df %>%
  #mutate(bins = BMAT_all) %>%
  mutate(bins = round(BMAT_all)) %>%
  group_by(bins) %>%
  mutate(offer_fraction = mean(Offer), n = n()) %>%
  ggplot(aes(bins, offer_fraction)) +
  geom_point(aes(x = BMAT_all, y = as.numeric(Offer))) +
  geom_point(colour = "red") +
  geom_line(colour = "red")
```


As you can see, we have 